\textbf{NBA Party}

### 2017-07-14 cardinal_analytx_presentation/nightlife_and_sports.tex
Condensed 'Data' section down to one slide!

@@

\begin{frame}   \frametitle{Anecdotal evidence: players do party}
  \begin{block}{Open attitude toward partying}     Matt Barnes recently complained, ``there's no nightlife in Utah'' when asked
    about playing the Jazz in the 2017 playoffs.\footnote{Cestone and Seiter ('17).}   \end{block}

@@

\begin{frame}   \frametitle{NBA data: 2010-11 through 2016-17 season}
  \begin{itemize}     \item Each team plays 82 games per season.
    \item 30 teams in the NBA.
    \item Total of $82 \times 30 / 2 = 1,230$ games per season.  
  \end{itemize}

  \vspace{12pt}We query \href{http://www.basketball-reference.com/leagues/}{basketball-reference.com}
  for a listing of game-days, and then 
  \href{http://www.covers.com/sports/NBA/matchups?selectedDate=2011-1-01}{covers.com} for 
  game-outcomes alongside a point-spread.

  \vspace{12pt}  
  \begin{itemize}     \item Missing the first couple months of 2010-11 season.
    \item At most two missing games in each of remaining seasons.
    \item Total of 7,829 games in our dataset.   \end{itemize}
\end{frame}

\begin{frame}   \frametitle{MLB data: 2011 through 2017 season}
  \begin{itemize}     \item Each team plays 162 games per season.
    \item 30 teams in the MLB.
    \item Total of $162 \times 30 / 2 = 2,430$ games per season.   \end{itemize}

  \vspace{12pt}We query \href{http://www.baseball-reference.com/leagues/}{baseball-reference.com}
  for a listing of game days, and again look to covers.com for game-outcomes and money-lines.

  \vspace{12pt}
  \begin{itemize}     \item We have on average 2,100 games per season.
    \item (Missing observations due to broken links, postponed games?)
    \item Total of 12,709 games in our dataset.    \end{itemize} \end{frame}

\begin{frame}   \frametitle{Bureau of Labor Statistics data: 2010-2016}
  We look toward BLS data which describes the number of business establishments 
  (of a very particular type) in each metropolitan statistical area
  for each quarter of each year.

  \vspace{12pt}  All teams are in the US with the exception of 
  \vspace{12pt}\begin{itemize}     \item Toronto Raptors (NBA)
    \item Toronto Blue Jays (MLB)   \end{itemize}

  \vspace{12pt}These two teams are excluded from our analysis.\footnote{We don't expect Toronto to be a huge party city.} \end{frame}

\begin{frame}   \frametitle{Minutes data for NBA}
  For NBA, we also collect minutes data from ESPN, which describes the number of 
  \vspace{12pt}
  \begin{itemize}     
    \item Free-throws
    \item Field goals
    \item Three-pointers   
  \end{itemize}
  \vspace{12pt}attempted and made by each player in each game. For each season and each team,
  we have nearly complete minutes data; 85\% of our season-teams have no more than 3 missing games. \end{frame}

>>>>

\begin{frame}   \frametitle{Anecdotal evidence: athletes party}
  \begin{block}{Open attitude toward partying}     Matt Barnes recently complained, ``there's no nightlife in Utah'' when asked
    about playing the Jazz in the 2017 playoffs.\footnote{Cestone and Seiter ('17).}   \end{block}

@@

@@

\begin{frame}   \frametitle{Data: 2010-11 through 2016-17}
  \begin{block}{NBA Data}     \begin{itemize}       \item Total of $82 \times 30 / 2 = 1,230$ games per season.
      % \item Missing the first couple months of 2010-11 season.
      \item Total of 7,829 games in our dataset.     \end{itemize}
  \end{block} 
  \begin{block}{MLB Data}     \begin{itemize}       \item Total of $162 \times 30 / 2 = 2,430$ games per season.
      % \item We have on average 2,100 games per season.
      \item Total of 12,709 games in our dataset.     \end{itemize}   \end{block}
  \begin{block}{BLS Data}
    \begin{itemize}       \item \# establishments by MSA-quarter-year.
      \item Excludes Toronto from our analysis.     \end{itemize}   \end{block}
  \begin{block}{ESPN Data}     \begin{itemize}       \item Describes \# shots taken for each player in each game.
      \item 85\% of our season-teams have no more than 3 missing games.     \end{itemize}   \end{block} \end{frame}
